Fractional Types

### 2016-12-18 typespp.tex
Some more on looping and delooping

\newcommand{\textpi}{$\pi$}
\newcommand{\ft}{\mathbb{T}}
\newcommand{\hash}{\#}
\newcommand{\pifrac}{\ensuremath{\Pi^/}}
\newcommand{\iso}{\leftrightarrow}
\newcommand{\isotwo}{\Leftrightarrow}
\newcommand{\alt}{~|~}
\newcommand{\ag}[2]{#1 \sslash #2}
\newcommand{\agp}[3]{#1 \sslash_{#3} #2}
\newcommand{\order}[1]{\hash #1}
\newcommand{\iorder}[1]{1/\hash #1}
\newcommand{\oneg}[1]{\mathbb{1}_{#1}}
\newcommand{\divgl}[2]{\hash{#1} \div_{l} \hash{#2}}
\newcommand{\divgr}[2]{\hash{#1} \div_{r} \hash{#2}}
\newcommand{\ord}[1]{\ensuremath{\mathsf{order}(#1)}}
\newcommand{\inl}[1]{\textsf{inl}(#1)}
\newcommand{\inr}[1]{\textsf{inr}(#1)}
\newcommand{\zt}{\mathbb{0}}
\newcommand{\ot}{\mathbb{1}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Zn}{\mathbb{Z}_n}
\newcommand{\Zvn}{\mathbb{Z}^v_n}
\newcommand{\N}{\mathbb{N}}
\newcommand{\cycle}{\textsf{cycle}}
\newcommand{\twod}{\mathbb{T}}
\newcommand{\fract}[2]{#1/#2}
\newcommand{\fv}[2]{\fcolorbox{black}{white}{\strut $#1$}\fcolorbox{black}{gray!20}{$\strut #2$}}
\newcommand{\pt}[2]{\bullet[#1,#2]}
\newcommand{\sing}[1]{\textsc{Sing}(#1)}
\newcommand{\singi}[2]{\textsc{SingI}_{{#1}}(#2)}
\newcommand{\iter}[1]{\textsc{Iter}(#1)}
\newcommand{\pair}[2]{\langle #1,#2 \rangle}
\newcommand{\triple}[3]{\langle #1,#2,#3 \rangle}
\newcommand{\distiterplus}[3]{\mathsf{dist}~#1~#2~#3}

@@

Our constructions of $\order{p}$ and $\iorder{p}$ are instances of a general pattern that we have instantiated to the setting of $\Pi$ and adapted to explicitly refer to weak (i.e., up to $\isotwo$ in our case) equivalences. In the general construction~\cite{looping}, a group $G$ is known to induce two groupoids, a looping groupoid $LG$ and a delooping groupoid $BG$. These are defined as follows.

The looping groupoid $LG$ has the group elements as objects and, for every
group elements~$g$ and $h$, there is a morphism between $g$ and $h^{-1} \cdot g
\cdot h$. If we fix a type $\tau$ and a particular 1-combinator $p : \tau \iso
\tau$, we get a group whose elements are the iterates $p^k$. The corresponding
looping groupoid would have all the iterates as objects and morphisms between
$p^{k_1}$ and $p^{k_2}$ whenever there exists an integer $j$ such that
$p^{k_2}$ is equivalent to $p^{-j} \odot p^{k_1} \odot p^{j}$. By
Lem.~\ref{lem:distiterplus}, the latter term is $\isotwo$-equivalent to
$p^{-j+k_1+j}$ which is $\isotwo$-equivalent to $p^{k_1}$. In other words, we
have a morphism between $p^{k_1}$ and $p^{k_2}$ whenever they are
$\isotwo$-equivalent which is consistent with our definition of iteration
groupoids. The delooping groupoid $BG$ has one trivial element and for each
group element $g$ a morphism from that element to itself. Modulo
$\isotwo$-equivalences, this is consistent with our definition of symmetry
groupoids.

>>>>

\newcommand{\textpi}{$\pi$}
\newcommand{\ft}{\mathbb{T}}
\newcommand{\hash}{\#}
\newcommand{\pifrac}{\ensuremath{\Pi^/}}
\newcommand{\iso}{\leftrightarrow}
\newcommand{\isotwo}{\Leftrightarrow}
\newcommand{\alt}{~|~}
\newcommand{\ag}[2]{#1 \sslash #2}
\newcommand{\agp}[3]{#1 \sslash_{#3} #2}
\newcommand{\order}[1]{\hash #1}
\newcommand{\iorder}[1]{1/\hash #1}
\newcommand{\oneg}[1]{\mathbb{1}_{#1}}
\newcommand{\divgl}[2]{\hash{#1} \div_{l} \hash{#2}}
\newcommand{\divgr}[2]{\hash{#1} \div_{r} \hash{#2}}
\newcommand{\ord}[1]{\ensuremath{\mathsf{order}(#1)}}
\newcommand{\inl}[1]{\textsf{inl}(#1)}
\newcommand{\inr}[1]{\textsf{inr}(#1)}
\newcommand{\zt}{\mathbb{0}}
\newcommand{\ot}{\mathbb{1}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Zn}{\mathbb{Z}_n}
\newcommand{\Zvn}{\mathbb{Z}^v_n}
\newcommand{\N}{\mathbb{N}}
\newcommand{\cycle}{\textsf{cycle}}
\newcommand{\twod}{\mathbb{T}}
\newcommand{\fract}[2]{#1/#2}
\newcommand{\fv}[2]{\fcolorbox{black}{white}{\strut $#1$}\fcolorbox{black}{gray!20}{$\strut #2$}}
\newcommand{\pt}[2]{\bullet[#1,#2]}
\newcommand{\sing}[1]{\textsc{Sing}(#1)}
\newcommand{\singi}[2]{\textsc{SingI}_{{#1}}(#2)}
\newcommand{\iter}[1]{\textsc{Iter}(#1)}
\newcommand{\pair}[2]{\langle #1,#2 \rangle}
\newcommand{\triple}[3]{\langle #1,#2,#3 \rangle}
\newcommand{\distiterplus}[3]{\mathsf{dist}~#1~#2~#3}
\newcommand{\looping}[1]{\mathcal{L}{#1}}
\newcommand{\delooping}[1]{\mathcal{B}{#1}}

@@

Our constructions of $\order{p}$ and $\iorder{p}$ are instances of a general
pattern that we have instantiated to the setting of $\Pi$ and adapted to
explicitly refer to weak (i.e., up to $\isotwo$ in our case) equivalences. In
the general construction~\cite{looping}, a group $G$ is known to induce two
groupoids, a looping groupoid $\looping{G}$ and a delooping groupoid
$\delooping{G}$. These are defined as follows.

The looping groupoid $\looping{G}$ has the group elements as objects and
morphisms between elements in the same conjugacy class, that is, there is a
morphism between elements $g$ and $h$ iff there exists a $x \in G$ such that
$g = x^{-1} \cdot g \cdot x$. Fixing a type $\tau$ and a particular 1-combinator
$p : \tau \iso \tau$, we get a group whose elements are the iterates $p^k$. The
corresponding looping groupoid has all the iterates as objects and morphisms
between $p^{k_1}$ and $p^{k_2}$ whenever there exists an integer $j$ such that
$p^{k_2}$ is equivalent to $p^{-j} \odot p^{k_1} \odot p^{j}$. By
Lem.~\ref{lem:distiterplus}, the latter term is $\isotwo$-equivalent to
$p^{-j+k_1+j}$ which is $\isotwo$-equivalent to $p^{k_1}$. In other words, we
have a morphism between $p^{k_1}$ and $p^{k_2}$ whenever they are
$\isotwo$-equivalent which is consistent with our definition of iteration
groupoids.

The delooping groupoid $\delooping{G}$ has one trivial element $\ast$, and for
each group element $g$ a morphism (loop) from $\ast$ to $\ast$. Modulo
$\isotwo$-equivalences, this is consistent with our definition of symmetry
groupoids.
